Reproducibility and plant pathology: where do we stand and a way forward

### 2021-06-16 analysis/paper/paper.Rmd
Embed fonts in figure 1.eps file

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 1.eps")
knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
```

>>>>

    Question->Methodology->Data->Analysis
    Analysis->Manuscript
    Methodology->Description
    Methodology->Citation
    Methodology->Availability
    Manuscript->Supplement
    Data->'Data File'->'Public Repository'
    Analysis->'Binary Code'->Supplement
    Analysis->'Source Code'->'Public Repository'
    Data->'Binary File'->Supplement
  }",
  width = 1000,
  height = 750
))
rsvg_ps(svg = charToRaw(p), file = "../figures/Sparks et al Figure 1.eps")
extrafont::embed_fonts(
   file = ("../figures/Sparks et al Figure 1.eps"),
   outfile = ("figures/Sparks et al Figure 1.eps"),
   options = "-dEPSCrop"
)
knitr::include_graphics(path = "../figures/Sparks et al Figure 1.eps")
```
